Data Cleaning

### 2025-12-10 Data Cleaning.Rmd
Added code to fit a model using just time of year.

>>>>

```{r}
library(tidymodels)
library(dplyr)
library(lubridate)

df_modeling <- df_lag_incdec |> 
  mutate(day = yday(Timestamp))

lm_model_spec <- linear_reg() |>
  set_engine("lm") |>
  set_mode("regression")

lm_recipe <- 
  recipe(FeCl_dose ~ day, data = df_modeling) |>
  step_poly(day, degree = 10)

lm_workflow <- workflow() |>
  add_model(lm_model_spec) |>
  add_recipe(lm_recipe)

lm_fit_result <- fit(lm_workflow, data = df_modeling)

predictions <- predict(lm_fit_result, new_data = df_modeling) |>
  bind_cols(df_modeling |> select(FeCl_dose))

rmse_result <- predictions |>
  rmse(truth = FeCl_dose, estimate = .pred)

mae_result <- predictions |>
  mae(truth = FeCl_dose, estimate = .pred)

print(rmse_result)
print(mae_result)
